---
title: "Analysis of video data from each run "
output:
  rmarkdown::html_document:
    theme: darkly
    fig_width: 10
    fig_height: 4
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
library(ggplot2)
library(dplyr)
library(plotrix)
library(readr)
library(knitrBootstrap)
library(knitr)



```


#  {.tabset}


## Introduction
Things which is been analysed throughout the project: </br>
  <ol>
   <li> Total views </li>
   <li> Total downloads </li>
   <li> Participants </li> 
   <li> Key factor derived from the data </br>
</ol>
## Video Titles

  1.1 Welcome to the course video <br>
  <font color="yellow">1.5 Privacy online and offline video </font> <br>
 1.14 Why would anyone want your data? <br>
 1.17 Preserving privacy in cloud storage: privacy by design video <br>
 1.19 Staying safe online: personal perspectives video <br>
  2.1 Welcome to Week 2: payment security<br>
  2.4	The evolving arms race of payment security<br>
 2.11 Exploring vulnerabilities in online payments<br>
 2.17 The million dollar contactless payment<br>
  3.1	Welcome to Week 3: security in the future home<br>
  3.2	Devices in the future home<br>
 3.14	Exploring security: biometric authentication<br>
 3.15	Exploring security: the Access Control Live Lab<br>
  
## Run 3

 <b> Total number of views is <font color="green"> 9607 </font></b> <br>
 <b> Total number of downloads <font color="green"> 756 </font></b><br>

```{r}
vidstats3 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-3_video-stats.csv")
tv <- sum(vidstats3$total_views)
Steps <- vidstats3$step_position
b <- vidstats3$total_downloads
c <- vidstats3$total_views
par(mfrow=c(1,2))
plot(Steps, b,
main="Downloads of videos",
ylab="",
type="l",
col="blue")

plot(Steps, c,
main="Total views of videos",
ylab="",
type="l",
col="red")

slices <- c(59.59,	4.12,	20.21,	6.69,	2.96,	5.79) 
lbls <- c("Europe", "Ocenia", "Asia", "North America", "South America", "Africa")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")

```
 
## Run 4

<b> Total number of views is <font color="green"> 10307 </font></b> <br>
 <b> Total number of downloads <font color="green"> 1054 </font></b><br>
 
```{r}
vidstats4 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-4_video-stats.csv")
Steps <- vidstats4$step_position
b <- vidstats4$total_downloads
c <- vidstats4$total_views
par(mfrow=c(1,2))
plot(Steps, b,
main="Downloads of videos",
ylab="",
type="l",
col="blue")

plot(Steps, c,
main="Total views of videos",
ylab="",
type="l",
col="red")

slices <- c(59.59,	4.12,	20.21,	6.69,	2.96,	5.79) 
lbls <- c("Europe", "Ocenia", "Asia", "North America", "South America", "Africa")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")
```

## Run 5

<b> Total number of views is <font color="green"> 10392 </font></b> <br>
 <b> Total number of downloads <font color="green"> 848 </font></b><br>
 
```{r echo=FALSE}
vidstats5 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-5_video-stats.csv")
Steps <- vidstats5$step_position
b <- vidstats5$total_downloads
c <- vidstats5$total_views
par(mfrow=c(1,2))
plot(Steps, b,
main="Downloads of videos",
ylab="",
type="l",
col="blue")

plot(Steps, c,
main="Total views of videos",
ylab="",
type="l",
col="red")

slices <- c(59.59,	4.12,	20.21,	6.69,	2.96,	5.79) 
lbls <- c("Europe", "Ocenia", "Asia", "North America", "South America", "Africa")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")
```

## Run 6

<b> Total number of views is <font color="green"> 5788 </font></b> <br>
 <b> Total number of downloads <font color="green"> 508 </font></b><br>
 
```{r echo=FALSE}
vidstats6 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-6_video-stats.csv")
Steps <- vidstats6$step_position
b <- vidstats6$total_downloads
c <- vidstats6$total_views
par(mfrow=c(1,2))
plot(Steps, b,
main="Downloads of videos",
ylab="",
type="l",
col="blue")

plot(Steps, c,
main="Total views of videos",
ylab="",
type="l",
col="red")

slices <- c(59.59,	4.12,	20.21,	6.69,	2.96,	5.79) 
lbls <- c("Europe", "Ocenia", "Asia", "North America", "South America", "Africa")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")


```

## Run 7

<b> Total number of views is <font color="green"> 5268 </font></b> <br>
 <b> Total number of downloads <font color="green"> 243 </font></b><br>

```{r echo=FALSE}
vidstats7 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-7_video-stats.csv")
Steps <- vidstats7$step_position
b <- vidstats7$total_downloads
c <- vidstats7$total_views
par(mfrow=c(1,2))
plot(Steps, b,
main="Downloads of videos",
ylab="",
type="l",
col="blue")

plot(Steps, c,
main="Total views of videos",
ylab="",
type="l",
col="red")

slices <- c(59.59,	4.12,	20.21,	6.69,	2.96,	5.79) 
lbls <- c("Europe", "Ocenia", "Asia", "North America", "South America", "Africa")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels 
lbls <- paste(lbls,"%",sep="") # ad % to labels 
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")

```

## Key Points
```{r echo = FALSE}
cse1 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-1_enrolments.csv")
cse2 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-2_enrolments.csv")
cse3 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-3_enrolments.csv")
cse4 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-4_enrolments.csv")
cse5 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-5_enrolments.csv")
cse6 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-6_enrolments.csv")
cse7 <- read.csv("~/Downloads/mooc-dataset-201920/cyber-security-7_enrolments.csv")
list1 <- list(9607,10307,10392,5788,5268)
list2 <- list(756, 1054, 848, 508, 243)
Run <- list(3,4,5,6,7)
par(mfrow=c(1,2))
plot(Run, list1,
main="Total viewers throughout the run",
ylab="",
type="l",
col="blue")

plot(Run, list2,
main="Total number of downloads throughout each run",
ylab="",
type="l",
col="red")

n1 <- nrow(cse1)
n2 <- nrow(cse2)
n3 <- nrow(cse3)
n4 <- nrow(cse4)
n5 <- nrow(cse5)
n6 <- nrow(cse6)
n7 <- nrow(cse7)

p <- list(n1,n2,n3,n4,n,n6,n7)
q <- list(1:7)

plot(Run, list2,
main="Total participants",
ylab="Participants",
xlab = "Run",
type="l",
col="red")

```






